Your main manuscript title

### 2021-06-16 forecast/paper/supplement.Rmd
add supplement and rebuilt figs

---
bibliography: [../../common/covidcast.bib]
output: 
  pdf_document:
    keep_tex: true
    template: pnas-suppl-template.tex
params:
  fd_casefloor: 30
  flag_jumps: 15
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 3,
                      fig.align = "center",
                      fig.path = "fig/",
                      cache = TRUE, 
                      autodep = TRUE,
                      message = FALSE, 
                      warning = FALSE)
source("eval_funs.R")
source("hotspot_funs.R")
source("trajectory_plots.R")
library(scales)
path_to_data <- "~/Documents/COVID-Delphi/fcast-indicators-paper/temp_data/"
```

@@

@@

```{r wis-densities}
ggplot(fcasts_honest %>% filter(period != "jm"), 
       aes(wis, fill = forecaster)) +
  geom_density() +
  scale_x_log10() +
  theme_bw(base_size = 12) +
  xlab("WIS") +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~forecaster) +
  theme(legend.position = "none")
```

@@

## Trajectories

@@

```{r hot-honest-v-finalized}
fig6b <- left_join(
  hotspots_honest %>%
    group_by(forecaster, ahead) %>%
    summarise(auc_honest = auc(value, actual)),
  hotspots_finalized %>%
    group_by(forecaster, ahead) %>%
    summarise(auc_finalized = auc(value, actual))) %>%
  ggplot(aes(ahead, auc_honest / auc_finalized, color = forecaster)) + 
  geom_line() + geom_point() +
  theme_bw(base_size = 12) + 
  scale_color_brewer(palette = "Set1", guide = guide_legend(nrow=1)) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_hline(yintercept = 1) +
  ylab("AUC (vintage / finalized)")
fig6b
```

@@

```{r figure5, eval = FALSE, fig.width=9, fig.height=4}
library(cowplot)
leg <- get_legend(fig5a)
fig5a <- fig5a + theme(legend.position = "none")
fig5b <- fig5b + theme(legend.position = "none")
fig5 <- plot_grid(fig5a, fig5b, align = "hv", nrow = 1)
fig5 <- plot_grid(fig5, leg, rel_heights = c(1,.1), nrow = 2)
fig5
```

@@

```{r figure6, fig.width=9, fig.height=4}
fig6a <- fig6a + theme(legend.position = "none")
fig6b <- fig6b + theme(legend.position = "none")
fig6 <- plot_grid(fig6a, fig6b, align = "hv", nrow = 1)
fig6 <- plot_grid(fig6, leg, rel_heights = c(1,.1), nrow = 2)
fig6
```

### Correlations with lagged actuals

```{r cor-with-actuals}
pct_change <- function(x, n = 14, col_name = "pct_change"){
  # courtesy of Alden
  dt <- c(0,-n)
  y = covidcast:::apply_shifts(x,dt) %>%
    rename(value = tidyselect::matches("value\\+"),
           lag_value = tidyselect::matches("value\\-")) %>%
    mutate(`:=`(!!col_name,(value - lag_value)/lag_value))
  return(y)
}
comparison_df <- left_join(
  fcasts_honest %>% filter(forecaster != "QAR3", period != "jm"),
  fcasts_honest %>% filter(forecaster == "QAR3", period != "jm") %>%
    select(-c(forecaster,target_end_date)) %>%
    rename(ar3_wis = wis),
  by = c("geo_value", "ahead", "forecast_date")) %>%
  group_by(forecaster, forecast_date, geo_value) %>%
  summarize(wis_ratio = mean(wis) / mean(ar3_wis), .groups = "drop")

@@

```{r cor-wis-ratio}
ggplot(pct_chng_df %>% 
         group_by(forecaster) %>% 
         mutate(median = median(cor_wisratio_pctchange)), 
       aes(x = cor_wisratio_pctchange)) +
  geom_histogram(aes(y = ..count.. / sum(..count..), fill = forecaster)) +
  scale_fill_brewer(palette = "Set1") +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_vline(aes(xintercept = median)) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  facet_wrap(~forecaster) + 
  xlab("Spearman correlation") + ylab("relative frequency") +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1))
```

```{r cor-wis-ratio-m1}
ggplot(pct_chng_df %>% 
         group_by(forecaster) %>% 
         mutate(median = median(cor_abs_wisratio_minus_1_pctchange)), 
       aes(x = cor_abs_wisratio_minus_1_pctchange)) +
  geom_histogram(aes(y = ..count.. / sum(..count..), fill = forecaster)) +
  scale_fill_brewer(palette = "Set1") +
  theme_bw(base_size = 14) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_vline(aes(xintercept = median)) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  facet_wrap(~forecaster) + 
  xlab("Spearman correlation") + ylab("Relative frequency") +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1))
```

@@

```{r up-down-processing}
preds <- readRDS(file.path(path_to_data, "predictions_honest.RDS"))
preds <- preds %>% 
  filter(abs(quantile - 0.5) < 1e-6) %>% 
  select(-quantile) %>%
  mutate(forecaster = recode(forecaster,
                             AR3 = "AR",
                             AR3CHCLI3 = "CHNG-CLI",
                             AR3CHCOV3 = "CHNG-COV",
                             AR3DVCLI3 = "DV-CLI",
                             AR3FBCLI3 = "CTIS-CLI-in-community",
                             AR3GSSAA3_Subset = "gs_subset",
                             AR3GSSAA3_Zero = "Google-AA",
                             Baseline = "strawman"
  )) %>%
  filter(! forecaster %in% c("gs_subset", "strawman"))

@@

```{r upswing-histogram}
df %>% 
  filter(period != "jm") %>%
  group_by(forecaster, geo_value, udf) %>%
  ggplot(aes(AR_wis - wis, fill = forecaster)) +
  geom_histogram(bins = 100) +
  facet_grid(udf ~ forecaster) +
  theme_bw(base_size = 14) +
  theme(legend.position = "none") +
  scale_fill_brewer(palette = "Set1") +
  scale_y_log10(breaks = c(10,1000,100000), 
                labels = trans_format("log10", math_format(10^.x))) +
  xlab("AR WIS - forecaster WIS") +
  geom_vline(xintercept = 0)
```

```{r upswing-histogram-logged}
df_summary <- df %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(m = GeoMean((AR_wis + 1) / (wis + 1)))
df %>% 
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  ggplot(aes((AR_wis + 1) / (wis + 1), fill = forecaster)) +
  geom_histogram(bins = 100) +
  facet_grid(udf ~ forecaster) +
  theme_bw(base_size = 14) +
  theme(legend.position = "none") +
  scale_fill_brewer(palette = "Set1") +
  scale_x_log10() +
  scale_y_log10(breaks = c(10,1000,100000), 
                labels = trans_format("log10", math_format(10^.x))) +
  xlab("AR WIS - forecaster WIS") +
  geom_vline(xintercept = 1) +
  geom_vline(data = df_summary, aes(xintercept = m), linetype = "dotted")
```

@@

lead_lag_metric <- lead_lag_metric %>%
  mutate(
    forecaster = recode(
      name,
      `value+0:chng_smoothed_adj_outpatient_cli` = "CHNG-CLI",
      `value+0:chng_smoothed_adj_outpatient_covid` = "CHNG-COV",
      `value+0:doctor-visits_smoothed_adj_cli` = "DV-CLI",
      `value+0:fb-survey_smoothed_hh_cmnty_cli` = "CTIS-CLI-in-community",
      `value+0:google-symptoms_sum_anosmia_ageusia_smoothed_search` = "Google-AA")) %>%
  ungroup() %>%
  select(-name)

@@

```{r leading-and-lagging, fig.width=8, fig.height=4}
df2 %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(
    leadingness = cor(AR_wis - wis, leading, use = "pairwise.complete.obs"),
    laggingness = cor(AR_wis - wis, lagging, use = "pairwise.complete.obs")) %>%
  pivot_longer(leadingness:laggingness) %>%
  ggplot(aes(udf, value, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(~name) +
  theme_bw(base_size = 14) +
  ylab("correlation") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

```{r diff-in-lead-lag, fig.width=8, fig.height=4}
df2 %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(cor = cor(AR_wis - wis, leading - lagging, 
                      use = "pairwise.complete.obs")) %>%
  ggplot(aes(udf, cor, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  geom_hline(yintercept = 0) +
  scale_fill_brewer(palette = "Set1") +
  theme_bw(base_size = 14) +
  ylab("correlation") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

>>>>

---
bibliography: [../../common/covidcast.bib, pnas-materials/pnas-sample.bib]
output: 
  pdf_document:
    keep_tex: true
    template: pnas-suppl-template.tex
params:
  fd_casefloor: 30
  flag_jumps: 15
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6.5, fig.height = 4.5,
                      fig.align = "center",
                      fig.path = "fig/",
                      cache = TRUE, 
                      out.width = "\\linewidth",
                      autodep = TRUE,
                      message = FALSE, 
                      warning = FALSE)
```

```{r source-funs, cache=FALSE}
source("../code/eval_funs.R")
source("../code/hotspot_funs.R")
source("../code/trajectory_plot_funs.R")
library(scales)
library(cowplot)
path_to_data <- "~/Documents/COVID-Delphi/fcast-indicators-paper/temp_data/"
```

@@

# Figures from results

@@

```{r wis-densities}
ggplot(fcasts_honest %>% filter(period != "jm"), 
       aes(wis, fill = forecaster)) +
  geom_density() +
  scale_x_log10() +
  theme_bw() +
  xlab("WIS") +
  scale_fill_manual(values = fcast_colors) +
  facet_wrap(~forecaster) +
  theme(legend.position = "none")
```

@@

## Trajectories (deprecated)

@@

```{r hot-honest-v-finalized}
fig6b <- left_join(
  hotspots_honest %>%
    group_by(forecaster, ahead) %>%
    summarise(auc_honest = auc(value, actual)),
  hotspots_finalized %>%
    group_by(forecaster, ahead) %>%
    summarise(auc_finalized = auc(value, actual))) %>%
  ggplot(aes(ahead, auc_honest / auc_finalized, color = forecaster)) + 
  geom_line() + 
  geom_point() +
  theme_bw() + 
  scale_color_manual(values = fcast_colors, guide = guide_legend(nrow=1)) +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  geom_hline(yintercept = 1) +
  ylab("AUC (vintage / finalized)")
fig6b
```

@@

```{r figure5}
leg <- get_legend(fig5a)
fig5a <- fig5a + theme(legend.position = "none")
fig5b <- fig5b + theme(legend.position = "none")
fig5 <- plot_grid(fig5a, fig5b, align = "hv", nrow = 1)
fig5 <- plot_grid(fig5, leg, rel_heights = c(1,.1), nrow = 2)
fig5
```

@@

```{r figure6}
fig6a <- fig6a + theme(legend.position = "none")
fig6b <- fig6b + theme(legend.position = "none")
fig6 <- plot_grid(fig6a, fig6b, align = "hv", nrow = 1)
fig6 <- plot_grid(fig6, leg, rel_heights = c(1,.1), nrow = 2)
fig6
```

## Correlations with lagged actuals

```{r cor-with-actuals}
pct_change <- function(x, n = 14, col_name = "pct_change"){
  # courtesy of Alden
  dt <- c(0,-n)
  y = covidcast:::apply_shifts(x,dt) %>%
    rename(value = tidyselect::matches("value\\+"),
           lag_value = tidyselect::matches("value\\-")) %>%
    mutate(`:=`(!!col_name,(value - lag_value)/lag_value))
  return(y)
}
comparison_df <- left_join(
  fcasts_honest %>% filter(forecaster != "AR", period != "jm"),
  fcasts_honest %>% filter(forecaster == "AR", period != "jm") %>%
    select(-c(forecaster,target_end_date)) %>%
    rename(ar3_wis = wis),
  by = c("geo_value", "ahead", "forecast_date")) %>%
  group_by(forecaster, forecast_date, geo_value) %>%
  summarize(wis_ratio = mean(wis) / mean(ar3_wis), .groups = "drop")

@@

```{r cor-wis-ratio}
ggplot(pct_chng_df %>% 
         group_by(forecaster) %>% 
         mutate(median = median(cor_wisratio_pctchange)), 
       aes(x = cor_wisratio_pctchange)) +
  geom_histogram(aes(y = ..count.. / sum(..count..), fill = forecaster)) +
  scale_fill_manual(values = fcast_colors) +
  theme_bw() +
  theme(legend.position = "none") +
  geom_vline(aes(xintercept = median)) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  facet_wrap(~forecaster) + 
  xlab("Spearman correlation") + ylab("Relative frequency") +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1))
```

```{r cor-wis-ratio-m1}
ggplot(pct_chng_df %>% 
         group_by(forecaster) %>% 
         mutate(median = median(cor_abs_wisratio_minus_1_pctchange)), 
       aes(x = cor_abs_wisratio_minus_1_pctchange)) +
  geom_histogram(aes(y = ..count.. / sum(..count..), fill = forecaster)) +
  scale_fill_manual(values = fcast_colors) +
  theme_bw() +
  theme(legend.position = "none") +
  geom_vline(aes(xintercept = median)) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  facet_wrap(~forecaster) + 
  xlab("Spearman correlation") + ylab("Relative frequency") +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1))
```

@@

```{r up-down-processing}
preds <- readRDS(file.path(path_to_data, "predictions_honest.RDS"))
preds <- preds %>% 
  filter(abs(quantile - 0.5) < 1e-6) %>% 
  select(-quantile) %>%
  mutate(forecaster = recode(forecaster,
                             AR3 = "AR",
                             AR3CHCLI3 = "CHNG-CLI",
                             AR3CHCOV3 = "CHNG-COV",
                             AR3DVCLI3 = "DV-CLI",
                             AR3FBCLI3 = "CTIS-CLIIC",
                             AR3GSSAA3_Subset = "gs_subset",
                             AR3GSSAA3_Zero = "Google-AA",
                             Baseline = "strawman"
  )) %>%
  filter(! forecaster %in% c("gs_subset", "strawman"))

@@

```{r upswing-histogram}
df %>% 
  filter(period != "jm") %>%
  group_by(forecaster, geo_value, udf) %>%
  ggplot(aes(AR_wis - wis, fill = forecaster)) +
  geom_histogram(bins = 100) +
  facet_grid(udf ~ forecaster) +
  theme_bw() +
  ylab("Count") +
  theme(legend.position = "none") +
  scale_fill_manual(values = fcast_colors) +
  scale_y_log10(breaks = c(10,1000,100000), 
                labels = trans_format("log10", math_format(10^.x))) +
  xlab("AR WIS - forecaster WIS") +
  geom_vline(xintercept = 0)
```

```{r upswing-histogram-logged}
df_summary <- df %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(m = GeoMean((AR_wis + 1) / (wis + 1)))
df %>% 
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  ggplot(aes((AR_wis + 1) / (wis + 1), fill = forecaster)) +
  geom_histogram(bins = 100) +
  facet_grid(udf ~ forecaster) +
  theme_bw() +
  ylab("Count") +
  theme(legend.position = "none") +
  scale_fill_manual(values = fcast_colors) +
  scale_x_log10() +
  scale_y_log10(breaks = c(10,1000,100000), 
                labels = trans_format("log10", math_format(10^.x))) +
  xlab("AR WIS - forecaster WIS") +
  geom_vline(xintercept = 1) +
  geom_vline(data = df_summary, aes(xintercept = m), linetype = "dotted")
```

@@

lead_lag_metric <- lead_lag_metric %>%
  mutate(
    forecaster = recode(
      name,
      `value+0:chng_smoothed_adj_outpatient_cli` = "CHNG-CLI",
      `value+0:chng_smoothed_adj_outpatient_covid` = "CHNG-COV",
      `value+0:doctor-visits_smoothed_adj_cli` = "DV-CLI",
      `value+0:fb-survey_smoothed_hh_cmnty_cli` = "CTIS-CLIIC",
      `value+0:google-symptoms_sum_anosmia_ageusia_smoothed_search` = "Google-AA")) %>%
  ungroup() %>%
  select(-name)

@@

```{r leading-and-lagging}
df2 %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(
    leadingness = cor(AR_wis - wis, leading, use = "pairwise.complete.obs"),
    laggingness = cor(AR_wis - wis, lagging, use = "pairwise.complete.obs")) %>%
  pivot_longer(leadingness:laggingness) %>%
  ggplot(aes(udf, value, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  geom_hline(yintercept = 0) +
  scale_fill_manual(values = fcast_colors) +
  facet_wrap(~name) +
  theme_bw() +
  ylab("Correlation") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

```{r diff-in-lead-lag}
df2 %>%
  filter(period != "jm") %>%
  group_by(forecaster, udf) %>%
  summarise(cor = cor(AR_wis - wis, leading - lagging, 
                      use = "pairwise.complete.obs")) %>%
  ggplot(aes(udf, cor, fill = forecaster)) +
  geom_bar(width = 0.6, position = position_dodge(width=0.6),
           stat = "identity") +
  geom_hline(yintercept = 0) +
  scale_fill_manual(values = fcast_colors) +
  theme_bw() +
  ylab("Correlation") +
  xlab("") +
  theme(legend.position = "bottom", legend.title = element_blank())
```

# Side figures (in their own scripts)

```{r ccf-dv-finalized}
library(covidcast)
source("../code/ccf-dv-finalized.R")
gg
```

```{r ny-trajectory}
source("../code/ny-trajectory.R")
gg
```

```{r revisions-dv-jhu}
source("../code/revisions-dv-jhu.R")
pp
```
